### 2018-08-21 introduction.tex
Paragraph about batch-wise and truly continuous approaches rewritten to resove issue #9

Liquid-fueled \gls{MSR} designs have online separations and/or feeds, where material is moved to or from the core at all times (continuous) or at specific time steps (batch). To account for batch discharge, a depletion tool must remove some or all material at specified intervals. This requires the burn-up simulation to stop at a given time and restart with a new liquid fuel composition (after removal of discarded materials and addition of fissile/fertile materials). Accounting for a continuous removal or addition is more difficult because it requires adding a term to the Bateman equations. In SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of Bateman equations using spectrum-averaged fluxes and cross sections generated from a deterministic transport calculation. Methods listed in references \cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013, rykhlevskii_online_2017} model true continuous feeds and removals, while other methods employ a batch-wise approach. \gls{ORNL} researchers have developed ChemTriton, a Python-based script for SCALE/TRITON which uses a semi-continuous batch process to simulate a continuous reprocessing. This tool models salt treatment, separations, discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON model over small time steps to simulate continuous reprocessing and deplete the fuel salt \cite{powers_new_2013}.

>>>>

Liquid-fueled \gls{MSR} designs have online separations and feeds, where material is moved to or from the core at specific time steps (batch) or continuously. In batch-wise approach the burn-up simulation stops at a given time and restart with a new liquid fuel composition (after removal of discarded materials and addition of fissile/fertile materials). \gls{ORNL} researchers have developed ChemTriton, a Python-based script for SCALE/TRITON which the batch-wise to simulate a continuous reprocessing. This tool models salt treatment, separations, discharge, and refill using a unit-cell \gls{MSR} SCALE/TRITON depletion simulation over small time steps to simulate continuous reprocessing and deplete the fuel salt \cite{powers_new_2013}. Methods listed in references \cite{fiorina_investigation_2013,sheu_depletion_2013,park_whole_2015, jeong_equilibrium_2016,powers_inventory_2014,betzler_molten_2017,rykhlevskii_online_2017} and current work employ a batch-wise approach.

Accounting for a continuous removal or addition is more difficult because it requires adding a term to the Bateman equations. In SCALE \cite{bowman_scale_2011}, ORIGEN \cite{gauld_isotopic_2011} solves a set of Bateman equations using spectrum-averaged fluxes and cross sections generated from a deterministic transport calculation. Approaches listed in references \cite{doligez_coupled_2014,heuer_towards_2014,aufiero_extended_2013,nuttin_potential_2005} model true continuous feeds and removals.
